Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
update infection status function with added recovery times

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
infection_status <- function(state, mean_crit_dist){

  current_infected <- state[state[,3]=='I',]
  current_suceptable <- state[state[,3]=='S',]
  current_removed <- state[state[,3]=='R',]
  current_non_infected <- rbind(current_suceptable, current_removed)

@@

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

>>>>

  #generated days of recovery times for each person
  recovery_days <- rpois(num_subjects,14)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist,t){

  current_infected <- state[state[,3]=='I',]
  current_suceptable <- state[state[,3]=='S',]
  current_removed <- state[state[,3]=='R',]

  current_recovered <- state[state[,3]=='Rec',]

  current_non_infected <- rbind(current_suceptable, current_removed)

@@

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])

      z_s <- as.numeric(current_recovered[i,'Rec'])

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      #check recovery time for person at z_s
      if(z_s>=t){
        new_status[j] <- 'Rec'
      }
      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

get_recovery_time <- function(){

}

@@

      r_times <-

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions
